term papaer 2

### 2024-02-12 outputs/paper/paper.qmd
paper

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
install.packages("here")
install.packages("dplyr") 
install.packages("tidyverse")
install.packages("rdrobust")
installed.packages("ggplot2")
# install.packages("knitr")

>>>>

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
install.packages("here")
install.packages("dplyr") 
install.packages("tidyverse")
installed.packages("ggplot2")
# install.packages("knitr")
